\subsubsection*{Why did you pick that habit?}
\begin{quote}
Participant 1: \textit{I was already doing meditation, but not the parts of meditation that were beneficial afterwards, I wasn't making it a habit. I wanted to not be stressed out of nut.}
\end{quote}
\begin{quote}
Participant 2: \textit{Want to be more flexible, easier habit, I am not going to do the plank every morning, it is easier with not too much effort, less time consuming.}
\end{quote}
\begin{quote}
Participant 3: \textit{I wanted to write in the morning, but half way through I changed to the later because I wasn't doing it.}
\end{quote}
\begin{quote}
Participant 4: \textit{It's something I wanted to do for a long time, so I thought this would help me make it more regular, I downloaded headspace meditation app, but it was hard to remember to actually do it. Using the bot in combination with headspace was good. Because headspace doesn't send me iphone reminders, chatbot is better with reminders because it is in messenger. So I was doing the habit with headspace while using chatbot.}
\end{quote}
\begin{quote}
Participant 5: \textit{It is something I wanted to do for a while, stress relief habit. Chance to give it a go for hope of it staying in the longer term.}
\end{quote}
\begin{quote}
Participant 6: \textit{Picked it because it is something that successful people do and I get stressed really easy.}
\end{quote}
\begin{quote}
Participant 7: \textit{I wanted to be more active and haven't had any exercise at all.}
\end{quote}

\subsubsection*{Are you still doing that habit?}
\begin{quote}
Participant 1: \textit{Meditation has been harder, but the first few days I was like, I now know how to do this. But if I got distracted it was harder to remember.}
\end{quote}
\begin{quote}
Participant 2: \textit{No not stretching.}
\end{quote}
\begin{quote}
Participant 3: \textit{No, just keep forgetting to do it or can't be bothered.}
\end{quote}
\begin{quote}
Participant 4: \textit{Yes, but, its not as regular, I do miss it.}
\end{quote}
\begin{quote}
Participant 5: \textit{I did it every now and again, usually I think about it, it depends, if I had a long day, sometimes I want to go to bed. Done it a couple of times, done it more when I was using the chatbot.}
\end{quote}
\begin{quote}
Participant 6: \textit{I do it when I remember, I tend to do it now before bed, rather than after lunch, only if I remember.}
\end{quote}
\begin{quote}
Participant 7: \textit{No, been out of town recently.}
\end{quote}

\subsubsection*{Did you like the chatbot?}
\begin{quote}
Participant 1: \textit{Neutral on it. Good that it let me know, but I am not sure about it.}
\end{quote}
\begin{quote}
Participant 2: \textit{Pretty good.}
\end{quote}
\begin{quote}
Participant 3: \textit{Yes I liked it. It has been great for reminding me to write.}
\end{quote}
\begin{quote}
Participant 4: \textit{Would've liked to of interacted with it a bit more, and to of been able to ask it for help and support throughout. Maybe it would tell you tips, like how to set aside some time to do things and ideas on how to meditate, where to go, different apps to use, or things like that. Liked to of had a bit more interaction with the bot.}
\end{quote}
\begin{quote}
Participant 5: \textit{Depending on my mood. If I was feeling okay it would remind me. Otherwise would get annoying, I ignored the message. If he said 'Not Yet', it would remind me sometimes when I already got to bed, (10.30pm), so needed a more precise time, maybe time boundaries.}
\end{quote}
\begin{quote}
Participant 6: \textit{Liked it because it reminded me 2 hours later! This other app that I used, didn't.}
\end{quote}
\begin{quote}
Participant 7: \textit{Yes, but was just always the same, repetitive. I was expecting different messages, like `Hey man' or `Hey [name]'. It needed to be a bit more caring about the person and a bit less like a robot.}
\end{quote}

\subsubsection*{How were the rewards?}
\begin{quote}
Participant 1: \textit{I didn't like the rewards, getting the GIF I was like, oh. I skipped over the GIF. I just wanted to get rid of the red dot on messenger. Because it was a bot, I just wanted to get rid of it. After the fourth time I saw same GIF it was bad. If it recognised my progress it would've been better. Based on my trend, my progress and if I done it on time. They didn't encourage me to move forward with my habit or set me back.}
\end{quote}
\begin{quote}
Participant 2: \textit{A bit weird, a bit funny, weird just a black screen. I liked the buttons that you could pick. But I didn't need a reward, it was unnecessary, the message was enough. Maybe use stats as they are cool, because you can reflect on data. Better to have info, like `you are almost there'.}
\end{quote}
\begin{quote}
Participant 3: \textit{Some of them were funny but maybe it works with other people and not me. I wanted different types of rewards and I didn't really like them. Maybe have, a measurement of something, if a person starts doing good, writing then give them their measurement, giving them constant well done's and stats. When they feel like they are making progress, they are more encouraged to keep doing it, rather than random music.}
\end{quote}
\begin{quote}
Participant 5: \textit{Cute, but I didn't think it gave me an intensive towards meditation, nice little extra. Not the sort of thing you want just before you go to bed, as I try to avoid the computer and phone before bed, not good for your sleep. But liked them.}
\end{quote}
\begin{quote}
Participant 7: \textit{I was always waiting to open them, the combination was perfect, it was funny. They were repetitive but not annoying.}
\end{quote}

\subsubsection*{Do you want it back?}
\begin{quote}
Participant 1: \textit{I am interested in having it back and it was good while it was there.}
\end{quote}
\begin{quote}
Participant 2: \textit{Yes, if it was enclosed in a Fitbit, because it would be all in one place.}
\end{quote}
\begin{quote}
Participant 3: \textit{Yes, but maybe, but only thing that I didn't like, was my reward.}
\end{quote}
\begin{quote}
Participant 4: \textit{Yes, if it had a bit more interaction with it, I would. In its current form, I wouldn't. It made me think I should download the headspace app on my phone. But the chatbot reminders were useful.}
\end{quote}
\begin{quote}
Participant 5: \textit{Would be more willing to give it a go if it had a more precise time, then yes.}
\end{quote}
\begin{quote}
Participant 6: \textit{Yes, definition. But I also downloaded an app that sends you a reminder, because they sent you a mindful message. But Harry's Habits had the snoozing `Not Yet' thing, that was better.}
\end{quote}
\begin{quote}
Participant 7: \textit{Yes. The bot was a helpful tool to remind me to do things.}
\end{quote}

\subsubsection*{Additional Comments}
\begin{quote}
Participant 1: \textit{Would be fine without rewards.}
\end{quote}
\begin{quote}
Participant 3: \textit{I participated in it to change my habits. Problem was with being consistent with a habit. I was very busy for a week and so didn't really write.}
\end{quote}
\begin{quote}
Participant 4: \textit{I felt like I needed the rewards. I wanted to put my own habit in and wanted drawing.}
\end{quote}
\begin{quote}
Participant 6: \textit{First few days were great, stuck to it. Bot was easy to setup. After a few days, I read the message and I would just do it later. Moved to new house and ran out of data, so got no data. Worked well at beginning, got worse and worse, still doing it, but it was at midnight.}
\end{quote}
\begin{quote}
Participant 7: \textit{I used the stretching as reminder for that and then to be more active, and go swimming. Sometimes I remember it, but don't always do it still. I want a chatbot to continue to help with my depression, my therapist said: every hour each day set alarm, saying how are you feeling right now, what are you feeling, is it based on reality or based on expectations? The chatbot for me, is very helpful to break my cycle, in my case, sometimes I get a thought and it cycles in my head, these things break this. After a while I stopped setting reminders, but only after 6 months, these repetitive things helped make a habit and helped me stick to a routine. But for this project, I wanted some different messages because otherwise, it is just an alarm that I had before. I want something more to replicate some sort of person.}
\end{quote}
