\section*{Executive Summary}

Habits are automatic actions that require little effort. The action of washing your hands automatically after using the toilet is an example of a positive habit. Positive habits grant many health benefits. To form a new positive habit, three elements are required: Repetition, contextual cues and positive reinforcement. The contextual cue acts as a trigger to push that person into performing the action and the positive reinforcement rewards the person encouraging them to perform the action again when triggered by the cue. After using these three elements the strength of a habit can be measured using a validated 12-question habit strength questionnaire that specifically looks at how automatic the action is after the trigger occurs. Literature uses this habit strength to show that using these three elements repetitively, on average, takes 66 days to form a new habit. However, studies show people still fail at forming new positive habits and many give up because people don't stick to a routine, straying away from the three elements.\newline
\newline
Mobile technology can help people stick to a routine for forming a habit that focuses on the three elements, by using reminders as the trigger, reminding us to repeat an action, helping us associate contextual information around the action and rewarding us with positive reinforcement. However most existing mobile apps are not grounded in theory and build repetitive actions rather than habit automaticity. Therefore, people become dependent on technology rather than the habit and when the system is eventually removed their habit performance decreases.\newline
\newline
Building habit automaticity is the key to removing this dependency and studies show motivation to complete the action increases habit automaticity and removes this dependency between the mobile technology and the user. We can encourage motivation with positive reinforcement by granting users satisfaction after completing the action. However what the reward is and how it is delivered is very important. Rewarding people with monetary gains (extrinsic rewards) hinders motivation, so rewards that benefit the person with satisfaction (intrinsic rewards) should be preferred. In addition, the type of reward should be delivered to suit each individual users needs, therefore a system should have a choice of reward delivery. Different research shows how interaction with users should span different modalities to suits the needs to users. This project will combine this knowledge from these two domains to focus on how intrinsic rewards from different modalities affects peoples habit strength.\newline
\newline
This project will use the three elements to build a mobile technology tool to deliver rewards from different modalities. These rewards will be delivered using a chatbot instead of a mobile app to present a novel method of interacting with users. Chatbots are a method of communicating with a computer system using natural language. They provide deeper integration into users mobile phone and can hook into messaging services users are familiar with, such as Facebook Messenger. The chatbot will be built using the three elements of habit formation, providing a vehicle for repetition, contextual cues and positive reinforcement.\newline
\newline
The chatbot design will be based on a combined set of theory-based design requirements. One for building habit formation apps that aim to increase habit automaticity and one for increasing motivation by delivering intrinsic rewards.\newline
\newline
A user study will evaluate the tool during a 30-day controlled test to measure users habit strength. Participants will engage daily with the bot for 30 days, then for a further 7 days all interaction with the bot will be stopped to test if users continue to perform their chosen habit after the bot is removed. The chatbot will provide habit tracking using reminders as triggers, and rewards from three modalities, visual, auditory and tactile vibration. Participants shall split into four groups, a control group will not receive rewards and the remaining three groups will each receive rewards from a single different modality. The user study will test the success of the chatbot by measuring users habit strength after the study, comparing the results with the control group.\newline
\newline
The project will deliver insight into how rewards from different modalities effect habit strength and opens up new research avenues for the investigating the use of chatbots as vehicles for promoting behaviour change.

\newpage

\section*{Definitions}

\textbf{Human-Computer Interaction (HCI)} - Field of computer science that studies how people interact with computers.\newline
\newline
\textbf{Modality} - In the context of HCI, a modality or mode is the classification of a single independent channel of sensory input or output between a computer and a human.\newline
\newline
\textbf{Multi-Modal Interaction} - Provides the user with multiple modalities or modes for interacting with a system.\newline
\newline
\textbf{Chatbot} - A method of communicating with a computer system via a conversation using natural language.

\newpage
