
\section*{Executive Summary}
Rewards motivate people to complete actions. Habit formation systems use rewards to motivate people to form habits. This thesis looks at the affect of three types of positive reinforcement rewards on habit formation delivered by a chatbot, from three modes: visual, auditory and visual-auditory combined. The findings are evaluated against two hypotheses: i) rewards effect on habit performance and automaticity, ii) multiple modalities effect on habit performance and automaticity. 60 people participated in a 4-week study followed by voluntary semi-structured interviews. The findings showed that participants receiving the bot-delivered rewards had higher habit performance than the control group without rewards. A correlation was found between the habit formation method and habit automaticity. However, all participants interviewed (N = 7) found a drop in habit performance after one week without the prototype. Further research for using different rewards with behaviour change technology is needed to validate how each modality affected habit automaticity and habit performance.

In summary this research produced four key deliverables.

\begin{enumerate}
  \item Review of existing behaviour change techniques and habit formation rewards with research into how they are used in technology.
  \item Design recommendations for building chatbots that deliver rewards in different modalities.
  \item Constructing Harry's Habits, a chatbot to track habits and deliver rewards from three modalities, visual, auditory and visual-auditory.
  \item Running and evaluating Harry's Habits in a 4-week trial with 60 participants to test how each reward impacted habit automaticity and habit performance.
\end{enumerate}

\newpage




\section*{Definitions}

\textbf{Human Computer Interaction (HCI)} - Field of computer science that studies how people interact with computers.\newline
\newline
\textbf{Modality} - In the context of HCI, a modality or mode is the classification of a single independent channel of sensory input or output between a computer and a human.\newline
\newline
\textbf{Chatbot} - A method of communicating with a computer system via a conversation.

\newpage
