\section*{Abstract}
Habits are automatic actions that require little effort. A simple action such as turning on the light to a room happens automatically, even if the light is already on.
Forming new positives habit needs three elements: contextual cues, positive
reinforcement and repetition.
The contextual cue acts as a trigger and the positive reinforcement rewards the
person encouraging them to perform the action again when triggered by the cue.
A study measured repetition to show a habit takes on average,
66 days to form~\cite{article_how_habits_formed_modelling_habit_formation}.
However, people still fail at forming new positive habits and give up because
they don't stick to a
routine~\cite{article_promoting_habit_formation, article_the_habitual_consumer}.\newline
\newline
Mobile technology can help people stick to a routine by focusing on the three elements.
Using reminders as triggers to repeat an action, helping us associate contextual
information around the action and rewarding us with positive reinforcement.
Yet most existing mobile systems aren't built on theory, leading to repetitive actions rather than habit automaticity.
Therefore, people become dependent on technology and habit performance decreases when the system is eventually removed.\newline
\newline
Building habit automaticity removes this dependency.
We can increase automaticity by building motivation to complete the action~\cite{article_a_self_efficacy, article_meta_analytic_review_intrinsic_motivation}
We can encourage motivation by rewarding users with positive reinforcement by granting user's satisfaction after completing the action.
However, reward type and delivery type are important. Giving money (extrinsic rewards) hinders motivation.
Giving satisfaction (intrinsic rewards) benefits the person and should be preferred.
The type of delivery should suit each individual user so a choice of delivery should be available.
Different research~\cite{article_user_centred_multimodal_reminders} shows how interaction with users should span different modalities to suit the needs to users.
This project will combine this knowledge from these two domains to focus on how intrinsic rewards from different modalities affect people's habit strength.\newline
\newline
This project will use the three elements of habit formation to build a mobile technology tool to deliver rewards from different modalities.
These rewards will be delivered using a chatbot instead of a mobile app to present a novel method of interacting with users.
Chatbots are a method of communicating with a computer system using natural language, providing deeper integration into users mobile phone and
can hook into messaging services users are familiar with, such as Facebook Messenger.
The chatbot will be built using the three elements of habit formation, delivering: contextual cues, positive reinforcement and repetition.
The chatbot design will be based on a combined set of theory-based design requirements;
one for building habit formation apps that aim to increase habit automaticity and one for increasing motivation with intrinsic rewards.\newline
\newline
An evaluation trial will test the chatbot tool during a 4-week controlled period to measure user's habit strength.
Participants will engage daily with the bot for 4 weeks, then for a further 1-week all interaction with the bot will be stopped to test
if users continue to perform their chosen habit after the bot is removed.
The chatbot will provide habit tracking using reminders as triggers, and rewards from three modalities, visual, auditory and tactile vibration.
Participants will split into four groups, a control group that will not receive any rewards and the remaining three groups that will each receive rewards from a single different modality.
The evaluation trial will test the success of the chatbot by measuring user's habit strength after the study, comparing the results with the control group.\newline
\newline
The project aims to deliver insight into how rewards from different modalities effect habit strength and opens up new research avenues for investigating the use of chatbots as
vehicles for promoting behaviour change.
\newpage

\section*{Definitions}

\textbf{Human-Computer Interaction (HCI)} - Field of computer science that studies how people interact with computers.\newline
\newline
\textbf{Modality} - In the context of HCI, a modality or mode is the classification of a single independent channel of sensory input or output between a computer and a human.\newline
\newline
\textbf{System with Different Modalities} - A system that provides the user with multiple modes of interaction.\newline
\newline
\textbf{Chatbot} - A method of communicating with a computer system via a conversation using natural language.

\newpage
