
\section{Limitations and Future Work} \label{limitations_and_future_work}
There were several limitations to these findings. Firstly, the evaluation of the second hypotheses relied on participants self-reporting. Participants could have simply lied to remove the alert and get the reward. This is particularly true with the snooze function, as some participants found it annoying and stopped using the chatbot over time. Participants may have been getting rid of the reminder rather than completing the habit, therefore the measurement could have been how participants reacted to notifications instead of if they competed their habit. Therefore, it is difficult to draw any valid conclusion on actual habit performance. Future work into how the platform participants used effected how quickly they responded to the alerts, e.g. browser, iOS or Android. Secondly, only seven participants responded to the follow up interviews for the evaluation of the first hypotheses although this might have been caused by the fact that these interviews were optional and not an integral part of the study. In addition, the study relied on participants recall, which could be inaccurate. Therefore, a larger sample size for the SRBAI questionnaire is needed to validate the hypotheses and the findings. Thirdly, additions to the chatbot, such as using natural language processing, could improve the functionality of the chatbot, proving a more conversational user interface and perhaps could increase participant interaction and perhaps not create a dependence between our prototype and participants habit performance during the 3-week period as this was disadvantage for habit formation. Fourthly, the small number of participants and the small sample of rewards used in the study make it unclear how these findings would generalise to other types of rewards with the same modality. Finally, these findings only apply to the intrinsic positive reinforcement rewards used in the study, as the content and method of delivery is another variable that effects these results. Additional studies using different types of bot-delivered rewards from different modalities would validate these findings.

\section{Conclusion}
We have surveyed three areas of literature: habit formation rewards, different modes of feedback and chatbot interaction. We found that habit performance and habit automaticity are keys to building lasting behaviour change. This thesis builds these three areas into a set of design requirements for building reward-based chatbots that support habit formation.
A prototype is designed and constructed from these requirements, that aims to track habits and deliver rewards from three modalities: visual, auditory and visual-auditory combined.
We evaluated our prototype during a 4-week study against two hypotheses, comparing these against a control group and each reward type: i) positive reinforcement is effective at supporting habit formation by increasing automaticity and regular habit performance, ii) multiple modalities rewards are more effective then singular mode rewards. Thirty-six participants completed the study interacting with the bot for three weeks to try and form a new positive habit, then for a further 1-week interaction with the prototype was suspended. Validated habit automaticity questionnaires and seven participant interviews were performed for further validation. This allowed us to evaluate how habit performance and habit automaticity was effected without technology. The results show how rewards delivered by Harry's Habits affected habit performance and habit automaticity.
More specifically,
the results found that the bot-delivered rewards improved habit performance; thus participants were more likely to complete their habit if given the reward. Habit performance was also affected by different modalities, although not in the way our hypotheses assumed, as singular modalities had higher habit performance than visual-auditory rewards. Finally, the findings of the study show there is no statistical significance whether the rewards or the combined modalities effected habit automaticity. More conclusive evidence is needed to show that rewards from combined modalities effect habit automaticity. Nevertheless, although there were limitations to this project, there is still a significant contribution with comparisons of visual, auditory and visual-auditory positive reinforcement rewards and we hope this may open up new research avenues for investigating the use of chatbots as tools to help form new habits.
